\documentclass[journal,transmag]{IEEEtran}

\hyphenation{op-tical net-works semi-conduc-tor}
\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
	pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
	colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
	pdftitle={Bare Demo of IEEEtran.cls for Computer Society Journals},%<!CHANGE!
	pdfsubject={Typesetting},%<!CHANGE!
	pdfauthor={Michael D. Shell},%<!CHANGE!
	pdfkeywords={Computer Society, IEEEtran, journal, LaTeX, paper, template}}

\begin{document}
	\title{Does Popularity Influence the Academy Awards?}
	\author{
		\IEEEauthorblockN{
			Fojan Babaali,
			Maryam Honari Jahromi,
			Omar Elazhary,
			Ali Mashreghi
		}
		\IEEEauthorblockA{
			\IEEEauthorrefmark{1}
			University of Victoria, Victoria, Canada
		}
	}
	\IEEEtitleabstractindextext{
		\begin{abstract}
			In this project we are going to predict whether a movie will win an Academy Award or not. Our main data is the Kaggel’s IMDB information on movies. However, we will add supplementary data about the history of Oscars' winners/nominees. We use the information after the movie was released since social media information -which is an important part of our features- only becomes stable a few months after release. We also intend to find the suitable algorithm to classify movies properly. Among the candidate algorithms are Naive bayes classifiers and linear regressors. We will also attempt to define a criteria by which movies are chosen.
		\end{abstract}
		\begin{IEEEkeywords}
			Oscars, Movies, Prediction, Classification, Machine Learning, Data Mining
		\end{IEEEkeywords}
	}
	\maketitle
	\IEEEdisplaynontitleabstractindextext
	\IEEEpeerreviewmaketitle
	
	\section{Introduction}
	
	
	\section{Related Work}
	
	
	\section{Data Gathering}
	
	
	\section{Methods}
	
		\subsection{Classification}
		
			\subsubsection{Support Vector Machines}
			
			\subsubsection{Logistic Regression}
			
			\subsubsection{Gaussian Naive Bayes}
			
			\subsubsection{AdaBoost}
			
			\subsubsection{Perceptrons}
			
			\subsubsection{Neural Networks (MLPs)}
			
		\subsection{Regression}
			
			\subsubsection{Support Vector Regressors (SVRs)}
			
			\subsubsection{AdaBoost}
			
			\subsubsection{Linear Regression}
	
	\section{Results}
	
	
	\section{Discussion}
	
	
	\section{Contributions}
	
	
\end{document}